### 2020-06-24 Documents/ESA/sections/LitReview.tex
minor mods in intro

@@

@@

\begin{enumerate}
    \item Distributed. It will often be the case that a multi-agent system must spread out across a
    large area or operate in regions where communication is limited. As such it is beneficial that
    such a system does not rely too heavily on communication with a central body. The individual
    agents must, therefore, be able to make their own decisions and act as independent entities.
    Aside from the advantage of communication, this ensures that the system is not tied to a single
    point of failure; in a system governed by a centralised decision maker, any faults in the
    central body propagates throughout the group. Of course, this comes at the price of
    computational load - if the agents are required to act independently, they must possess the
    resources to do so. The term distributed should not be confused with decentralised. The latter
    refers to a regime in which agents all communicate with one another before making a decision.
    Whilst this is preferable to a centralised decision maker in terms of the requirement for one
    entity to communicate with all agents, it still places a high cost on the requirement that
    agents be in constant communication with one another. In fact it may pose the additional risk
    that if any agent in the team fails, the whole pipeline falls apart. Distributivity, on the
    other hand, requires that agents make independent decisions so that, though agents may
    communicate with each other, they are still able to operate when this is not possible.
    \item Generality. MAS come in many different flavours; sometimes a small group of heterogeneous 
    (agents with different capabilities) agents may be required to perform a delicate task whilst
    in others, it may be required that a large population of homogeneous (all of the same type)
    agents perform multiple tasks simultaneously. Indeed the same MAS may have to adapt its
    strategy whilst in the middle of a task. It would be a hindrance if the agents were required to
    be reprogrammed with a completely different control methodology each time the situation changes
    slightly. It would be preferable if the method could apply to all different types of scenarios,
    with homogenous or heteregeneous agents, with single tasks or multiple, in any environment with
    only minor customisation required. Better still if the agents are able to adapt themselves to
    the specifics of the scenario.
    \item Low Computational Load. As mentioned in the previous chapter, a MAS will often be used in
    complex situations, many of which will be too dangerous for human intervention. As such, the
    system will be required to carry out its tasks online. For this reason, it is vital that the
    control method be one which produces low computational load - especially where the time frame
    for adjusting agent behaviour is limited. Monetary concerns also play a part in this metric; it
    would not do to impose that every member of the team be equipped with high performance computing
    power as this would likely fall outside of the budget of any practical usage.
    \item Robustness. Particularly for physical robots, a MAS should be able to operate in
    situations which present sensor noise, communication noise, latency, and environmental
    disturbances. This is rather important in unseen environments where full a priori knowledge of
    the map cannot be assumed.
    \item Scalable. This is mentioned last since the ability for a MAS to scale comes from its
    distributivity  and low computational load. Scalability is the capacity for any method of
    controlling a MAS to successfully operate as the size of the team increases. This, of course, is
    related to the complexity of the algorithms involved. However, it should be noted that it is not
    always required that a MAS be formed of dozens (or even hundreds) of agents. Depending on the
    task at hand (e.g. robotic surgery), it may be beneficial for fewer, more capable agents to
    perform the task, rather than a large population. 
\end{enumerate}

@@

Game Theory has a rich history when considering an understanding of multi-agent systems and it
is impossible to examine MAS without an understanding of Game Theory. These
begin in economics but have found a strong application in computation due to the rising need for
distributed systems. Game Theory, therefore, branches across all of the categories in this
chapter although its synergy with swarms requires development) since Dec-POMDP
and MARL methods have both base their theory upon the foundations of Game Theory.

@@

POSGs act as a game theoretic corollary to the Dec-POMDP. Here, an optimal solution is found by
fixing the strategy (a manner of selecting an action \cite{Rizk2018}) of all agents
except one. The optimal strategy of the chosen agent is then computed. This is fixed so that the
next agent may determine its optimal strategy. This process is iterated over all agents in a process
known as Alternating Maximisation \cite{Ray2010}. By choosing strategies which maximise
a common payoff, a globally optimal solution can be found.

@@

Mylvaganam et al, in \cite{Mylvaganam2017AutonomousApproach}, consider the N-robot collision
avoidance problem, similarly from the point of view of differential game theory. They develop a
robust feedback system for the robots which they show to be able to drive the system towards
predefined targets whilst providing guarantees of interference from other agents (or lack thereof).
In \cite{MylvaganamASystems}, Mylvaganam also considers a game theoretic control of multi-agent
systems in a distributed manner. Here, agents only consider their own payoff structure and have
limited communication with one another. The author shows that an approximate equilibrium can be
found using algebraic methods and illustrate the capabilities of the technique using a collision
avoidance example. For the sake of brevity the numerous contributions that Mylvaganam has made to
this field is not presented here. However, we will conclude with those presented in
\cite{Mylvaganam2014}. Here, the author presents approximate solutions to a number of differential
games, including linear-quadratic differential games (in which system dynamics are linear functions
whilst payoff functions are quadratic), Stackelberg differential games, where a hierarchy is 
induced across the players (a notion was suggested in the research proposal) and mean-field games,
which is discussed in 'MARL'. The importance of the linear-quadratic
differential game is the stability of the solution; solutions for the Nash equilibria (NE) are
admissable iff they are locally exponentially stable (which the author often shows with the aid of
Lyapunov functions). Approximate solutions to the NE are developed which are more feasible to
calculate online. The author then shows that this is not simply a theoretical exercise by applying
the novel methods towards multi-agent collision problems and designs dynamic control laws which
guarantee that each agent will reach their desired state whilst avoiding collision with the other
agents. Similarly, the Stackelberg game is applied to the problem of optimal monitoring by a multi
robot system.

@@

The task of MARL is to determine an optimal joint policy for all agents across the game. This joint
policy may be the concatenation of all the individual policy or it may just be options for each
agent to take. In either case, optimality is defined through the standard notions of Nash equilibria
and so, in this section, I will try to consider the broad spectrum of methods which attempt to
achieve this Nash equilibria. The largest problem in MARL is the non-stationarity of the environment
\cite{Hernandez-LealA}. In single-agent settings, it is assumed that the environment is Markovian.
However, this must be lifted in the Multi Agent setting since other agents in the environment will
be learning concurrently. As such, we must now consider that the policy for any one agent will
depend on the policy of all other agents.

@@

The most fundamental method to learning in Matrix games is the simplex algorithm. This is a popular
method of linear programming (in which constraints are linear). This will be important in
considering more current methods. A similar consideration is given to the infinitesimal gradient
ascent algorithm, in which the step size converges to zero. This method guarantees that, in the
infite horizon limit, the payoffs will converge to the Nash equilibrium payoff. Note that this does
not necessarily mean that both agents will converge to a single Nash equilibrium. This is a
particular problem in games where there are multiple Nash equilibria. However, in practice it is
difficult to choose a convergence rate of the step size and, without an appropriate choice the
strategy may oscillate as shown in the book. To address this, a modified approach is presented by
Bowling and Veloso which incorporates the notion of Win or Learn Fast (WoLF) to produce WoLF-IGA
\cite{Bowling2002}.
WoLF is a notion we will come across often in MARL and is shown by the authors to converge to always
to a NE. The concern with WoLF methods, however, is that it requires explicit knowledge of the
payoff matrix (which is not so much of a problem for model based methods) and the opponent's
strategy (which is more of a problem in real-world methods). Finally, the Policy Hill Climbing
method (PHC) is shown to converge to an optimal mixed strategy if the other agents are stationary
(i.e. are not learning). However, it is shown that, when this is not the case, the algorithm again
oscillates. The WoLF-PHC adaptation of this method is shown to converge to a NE strategy for both
players with minimal oscillation.

@@

Stochastic Games (or Markov Games) form a basis for MARL settings. However, in this case the agents
must learn about the equilibrium strategies by playing the game, which means they do not have a
priori knowledge of the reward or transition functions. Schwarz considers two properties which
should be used for evaluating MARL algorithm: rationality and convergence. The latter simply states
that the method should converge to some equilibrium whereas the former suggests that the method
should learn the best response to stationary opponents. A similar set of conditions is considered by
Conitzer and Sandholm in \cite{ConitzerAWESOME:}, whose algorithm we will consider shortly. Schwarz
then presents a review of MARL methods (as of September 2014)

@@

Multi Agent Learning Dynamics (often referred to as Game Dynamics or Learning Dynamics)
considers the
problem of mathematically modelling Multi Agent Systems who adapt through repeated interact with one
another. This model then serves to be able to predict the evolution of the system as well as to
understand the trajectory of learning. Typically, this looks at considering whether or not the
method is likely to converge towards a Nash equilibrium. This is generally a difficult problem to
solve \cite{ShohamMultiagentFoundations} for all but toy problems.
\cite{Letcher2019DifferentiableMechanics} shows that the stable equilbrium and Nash equilibrium (NE)
are not necessarily the same and, in fact, argue that stable points are more informative than NEs.
Stability provides some guarantees against the stochastic nature of the environment since a stable
equilibrium will always be returned to even after perturbations. This extremely important in Safe
and Trusted AI as it provides guarantees against undesired behaviour in real world environments.

@@

\section{Remarks} \label{sec:remarks}

>>>>

\fr{you might provide an overview of the introduction with the
  different sections.}

@@

\fr{I wonder whether this section would fit better in Intro.}

@@

\begin{enumerate}
    \item {\em Distributed}. It will often be the case that a
      multi-agent system must spread out across a large area or
      operate in regions where communication is limited. As such it is
      beneficial that such a system does not rely too heavily on
      communication with a central body. The individual agents must,
      therefore, be able to make their own decisions and act as
      independent entities.  Aside from the advantage of
      communication, this ensures that the system is not tied to a
      single point of failure; in a system governed by a centralised
      decision maker, any faults in the central body propagates
      throughout the group. Of course, this comes at the price of
      computational load - if the agents are required to act
      independently, they must possess the resources to do so. The
      term distributed should not be confused with decentralised. The
      latter refers to a regime in which agents all communicate with
      one another before making a decision.  Whilst this is preferable
      to a centralised decision maker in terms of the requirement for
      one entity to communicate with all agents, it still places a
      high cost on the requirement that agents be in constant
      communication with one another. In fact it may pose the
      additional risk that if any agent in the team fails, the whole
      pipeline falls apart. Distributivity, on the other hand,
      requires that agents make independent decisions so that, though
      agents may communicate with each other, they are still able to
      operate when this is not possible.

    \item {\em Generality}. MAS come in many different flavours; sometimes a
      small group of heterogeneous
      %(agents with different capabilities)
      agents may be required to perform a delicate task
      whilst in others, it may be required that a large population of
      homogeneous
      %(all of the same type)
      agents perform multiple tasks
      simultaneously. Indeed the same MAS may have to adapt its
      strategy whilst in the middle of a task. It would be a hindrance
      if the agents were required to be reprogrammed with a completely
      different control methodology each time the situation changes
      slightly. It would be preferable if the method could apply to
      all different types of scenarios, with homogenous or
      heteregeneous agents, with single tasks or multiple, in any
      environment with only minor customisation required. Better still
      if the agents are able to adapt themselves to the specifics of
      the scenario.

\item {\em Low Computational Load}. As mentioned in the previous chapter, a
  MAS will often be used in complex situations, many of which will be
  too dangerous for human intervention. As such, the system will be
  required to carry out its tasks online. For this reason, it is vital
  that the control method be one which produces low computational load
  - especially where the time frame for adjusting agent behaviour is
  limited. Monetary concerns also play a part in this metric; it would
  not do to impose that every member of the team be equipped with high
  performance computing power as this would likely fall outside of the
  budget of any practical usage.

    \item {\em Robustness}. Particularly for physical robots, a MAS
      should be able to operate in situations which present sensor
      noise, communication noise, latency, and environmental
      disturbances. This is rather important in unseen environments
      where full a priori knowledge of the map cannot be assumed.

    \item {\em Scalable}. This is mentioned last since the ability for
      a MAS to scale comes from its distributivity and low
      computational load. Scalability is the capacity for any method
      of controlling a MAS to successfully operate as the size of the
      team increases. This, of course, is related to the complexity of
      the algorithms involved. However, it should be noted that it is
      not always required that a MAS be formed of dozens (or even
      hundreds) of agents. Depending on the task at hand (e.g. robotic
      surgery), it may be beneficial for fewer, more capable agents to
      perform the task, rather than a large population.
\end{enumerate}

@@

Game Theory has a rich history when considering an understanding of
multi-agent systems and it is impossible to examine MAS without an
understanding of Game Theory. These begin in economics but have found
a strong application in computation due to the rising need for
distributed systems. Game Theory, therefore, branches across all of
the categories in this chapter although its synergy with swarms
requires development\fr{)?} since Dec-POMDP \fr{not yet defined} and MARL methods have both base
their theory upon the foundations of Game Theory.

\fr{we might want to motivate the restriction to partial observability. Dimension to add to the presentation of MAS?}

@@

POSGs act as a game theoretic corollary to the Dec-POMDP. Here, an
optimal solution \fr{to what?} is found by fixing the strategy (a
manner of selecting an action \cite{Rizk2018}) of all agents except
one. The optimal strategy of the chosen agent is then computed. This
is fixed so that the next agent may determine its optimal
strategy. This process is iterated over all agents in a process known
as Alternating Maximisation \cite{Ray2010}. By choosing strategies
which maximise a common payoff, a globally optimal solution can be
found.

@@

Mylvaganam et al, in \cite{Mylvaganam2017AutonomousApproach}, consider
the $N$-robot collision avoidance problem, similarly from the point of
view of differential game theory. They develop a robust feedback
system for the robots which they show to be able to drive the system
towards predefined targets whilst providing guarantees of interference
from other agents (or lack thereof).  In \cite{MylvaganamASystems},
Mylvaganam also considers a game theoretic control of multi-agent
systems in a distributed manner. Here, agents only consider their own
payoff structure and have limited communication with one another. The
author shows that an approximate equilibrium can be found using
algebraic methods and illustrate the capabilities of the technique
using a collision avoidance example. For the sake of brevity the
numerous contributions that Mylvaganam has made to this field is not
presented here. However, we will conclude with those presented in
\cite{Mylvaganam2014}. Here, the author presents approximate solutions
to a number of differential games, including linear-quadratic
differential games (in which system dynamics are linear functions
whilst payoff functions are quadratic), Stackelberg differential
games, where a hierarchy is induced across the players (a notion was
suggested in the research proposal) and mean-field games, which are
discussed under `MARL'. The importance of the linear-quadratic
differential game is the stability of the solution; solutions for the
Nash equilibria (NE) are admissable iff they are locally exponentially
stable (which the author often shows with the aid of Lyapunov
functions). Approximate solutions to the NE are developed which are
more feasible to calculate online. The author then shows that this is
not simply a theoretical exercise by applying the novel methods
towards multi-agent collision problems and designs dynamic control
laws which guarantee that each agent will reach their desired state
whilst avoiding collision with the other agents. Similarly, the
Stackelberg game is applied to the problem of optimal monitoring by a
multi robot system.

@@

The task of MARL is to determine an optimal joint policy for all
agents across the game. This joint policy may be the concatenation of
all the individual policy or it may just be options for each agent to
take. In either case, optimality is defined through the standard
notions of Nash equilibria and so, in this section, I will try to
consider the broad spectrum of methods which attempt to achieve
Nash equilibria. The largest problem in MARL is the non-stationarity
of the environment \cite{Hernandez-LealA}. In single-agent settings,
it is assumed that the environment is Markovian.  However, this must
be lifted in the Multi Agent setting since other agents in the
environment will be learning concurrently. As such, we must now
consider that the policy for any one agent will depend on the policy
of all other agents.

@@

The most fundamental method to learning in Matrix games is the simplex
algorithm. This is a popular method of linear programming (in which
constraints are linear). This will be important in considering more
current methods. A similar consideration is given to the infinitesimal
gradient ascent algorithm, in which the step size converges to
zero. This method guarantees that, in the infite horizon limit, the
payoffs will converge to the Nash equilibrium payoff. Note that this
does not necessarily mean that both agents will converge to a single
Nash equilibrium. This is a particular problem in games where there
are multiple Nash equilibria. However, in practice it is difficult to
choose a convergence rate of the step size and, without an appropriate
choice the strategy may oscillate as shown in the book \fr{please add ref}. To address
this, a modified approach is presented by Bowling and Veloso which
incorporates the notion of Win or Learn Fast (WoLF) to produce
WoLF-IGA \cite{Bowling2002}.  WoLF is a notion we will come across
often in MARL and is shown by the authors to converge to always to a
NE. The concern with WoLF methods, however, is that it requires
explicit knowledge of the payoff matrix (which is not so much of a
problem for model based methods) and the opponent's strategy (which is
more of a problem in real-world methods). Finally, the Policy Hill
Climbing method (PHC) is shown to converge to an optimal mixed
strategy if the other agents are stationary (i.e.~are not
learning). However, it is shown that, when this is not the case, the
algorithm again oscillates. The WoLF-PHC adaptation of this method is
shown to converge to a NE strategy for both players with minimal
oscillation.

@@

Stochastic Games (or Markov Games) form a basis for MARL
settings. However, in this case the agents must learn about the
equilibrium strategies by playing the game, which means they do not
have a priori knowledge of the reward or transition functions. Schwarz
considers \fr{where?} two properties which should be used for evaluating MARL
algorithm: rationality and convergence. The latter simply states that
the method should converge to some equilibrium whereas the former
suggests that the method should learn the best response to stationary
opponents. A similar set of conditions is considered by Conitzer and
Sandholm in \cite{ConitzerAWESOME:}, whose algorithm we will consider
shortly. Schwarz then presents a review of MARL methods (as of
September 2014)

@@

Multi Agent Learning Dynamics (often referred to as Game Dynamics or
Learning Dynamics) considers the problem of mathematically modelling
Multi Agent Systems who adapt through repeated interact with one
another. This model then serves to be able to predict the evolution of
the system as well as to understand the trajectory of
learning. Typically, this looks at considering whether or not the
method is likely to converge towards a Nash equilibrium. This is
generally a difficult problem to solve
\cite{ShohamMultiagentFoundations} for all but toy problems.
\cite{Letcher2019DifferentiableMechanics} shows that the stable
equilbrium and Nash equilibrium (NE) are not necessarily the same and,
in fact, argue that stable points are more informative than NEs.
Stability provides some guarantees against the stochastic nature of
the environment since a stable equilibrium will always be returned to
even after perturbations. This feature is extremely important in Safe
and Trusted AI as it provides guarantees against undesired behaviour
in real world environments.

@@

\section{Discussion} \label{sec:remarks}
